EinsteinPy: Python for General Relativity\footnote{Released on July, 15th, 2019}

### 2019-07-14 paper.tex
hypersurface abstract added

The heart of abstraction that EinsteinPy aims to provide is achieved by some set of data structures that are specifically designed to ease with varieties of gravitational physics problems. The most important and central quantity in all of the general relativity is the metric tensor $g_{\mu\nu}$ which defines the background geometry of spacetime on which all the dynamics happen. Informally the problem that packages of numerical relativity tend to solve is that we have a system (or matter field) defined by energy-momentum tensor $T_{\mu\nu}$ and we want to solve for the $g_{\mu\nu}$ such that it satifies the following Einstein's field equation

@@

\]where $R_{\mu\nu}$ is contracted Riemannian tensor or Ricci tensor, $R$ is Ricci scalar $\Lambda$ is cosmological constant. All the above quantities are derivatives of metric tensor\footnote{more on this can be refered from any standard general relativity text} so in simple terms, on the left hand side of the equation are terms involving $g_{\mu\nu}$ and on the right hand side are the matter field terms which only characterize the distribution of matter because of which the spacetime geometry is curved.\\

@@

@@

# calculates the trajectory
ans = obj.calculate_trajectory(
    end_lambda=end_lambda, OdeMethodKwargs={"stepsize": stepsize}, return_cartesian=True
)
\end{minted}
\subsection{plotting}
\subsection{symbolic}
\subsection{hypersurface}

>>>>

The heart of abstraction that EinsteinPy aims to provide is achieved by some set of data structures that are specifically designed to ease with variety of gravitational physics problems. The most important and central quantity in all of the general relativity is the metric tensor $g_{\mu\nu}$ which defines the background geometry of spacetime on which all the dynamics happen. Informally the problem that packages of numerical relativity tend to solve is that we have a system (or matter field) defined by energy-momentum tensor $T_{\mu\nu}$ and we want to solve for the $g_{\mu\nu}$ such that it satifies the following Einstein's field equation

@@

\]where $R_{\mu\nu}$ is contracted Riemannian tensor or Ricci tensor, $R$ is Ricci scalar, $\Lambda$ is cosmological constant. All the above quantities are derivatives of metric tensor\footnote{more on this can be refered from any standard general relativity text} so in simple terms, on the left hand side of the equation are terms involving $g_{\mu\nu}$ and on the right hand side are the matter field terms which only characterize the distribution of matter.\\

@@

\subsection{tensor}

@@

# calculates the trajectory
ans = obj.calculate_trajectory(
    end_lambda=end_lambda, OdeMethodKwargs={"stepsize": stepsize}, return_cartesian=True
)
\end{minted}
\subsection{plotting}
\subsection{symbolic}
\subsection{hypersurface}
This module provides with basic computational functions which are essential for modelling the space-like hypersurface for any spacetime geometry. Currently module has implementation for Schwarzschild geometry with conversion functions from Schwarzschild coordinates to 3-D spherical coordinates and some plotting utilities. The whole module is expected to extend for providing a superclass for implementations related to gravitationl lensing simulations and numerical calculations of null geodesics on hypersurfaces and deviation angles for systems which are relevant to relativistic astrophysical problems. A small code snippet for plotting the hypersurface is as follows:
\begin{minted}[linenos]{python}
# importing the modules
from einsteinpy.hypersurface import SchwarzschildEmbedding
from astropy import units as u

# Declaring embedding object with specified mass of the body 
surface_obj = SchwarzschildEmbedding(5.927e23 * u.kg)
surface_obj.plot_hypersurface(plot_type='surface')

# plotting the embedding hypersurface for Schwarzschild spacetime
surface_obj.show()
\end{minted}
\includegraphics[scale=0.5]{hypersurface_surface.png}
